Open archaeology, open source?

### 2023-09-20 analysis/_03-data_methodology.qmd
Fix open-archaeo to JOAD release
And rerender manuscript

# Methods & Materials <!-- Methods & Materials -->
<!-- TODO: snappier title? Maybe incoroporating 'open-archaeo'? -->

Our study comprises an exploratory analysis of open-archaeo, a list of open source archaeological software and other digital resources. As of right now it includes 408 items, which are rendered for the web at [open-archaeo.info](open-archaeo.info). We compiled the dataset by browsing collaborative software development platforms such as GitHub, GitLab and Codeberg, and by tracing connections to other personal, professional, and institutional websites that describe and host additional archaeological software. This entailed manually crawling through users' profiles, particularly those who identify as archaeologists or who have contributed to tools that pertain to archaeological work. We supplemented this quasi-systematic collection strategy with word-of-mouth contributions made by interested individuals who identified relevant work that we initially overlooked.

@@

```{r data-oarch}
read_csv("https://raw.githubusercontent.com/zackbatist/open-archaeo/master/open-archaeo.csv") %>%
  mutate(category = na_if(category, "?")) ->
  oarch

@@

```{r tbl-repo-licenses}
#| tbl-cap: Summary of licenses used by projects with GitHub repositories.
oarch |>
  hoist(gh_repo_info, license = list("license", 1, "name")) |>
  count(license) |>
  mutate(license = replace_na(license, "None detected"))
  arrange(-n) |>
  gt() |>
    cols_label(license = "License", n = "N")
```

>>>>

---
bibliography: references.bib
---

# Methods & Materials <!-- Methods & Materials -->

<!-- TODO: snappier title? Maybe incoroporating 'open-archaeo'? -->

Our study comprises an exploratory analysis of open-archaeo [@batist2023], a list of open source archaeological software and other digital resources.
As of right now it includes 408 items, which are rendered for the web at [open-archaeo.info](open-archaeo.info).
We compiled the dataset by browsing collaborative software development platforms such as GitHub, GitLab and Codeberg, and by tracing connections to other personal, professional, and institutional websites that describe and host additional archaeological software.
This entailed manually crawling through users' profiles, particularly those who identify as archaeologists or who have contributed to tools that pertain to archaeological work.
We supplemented this quasi-systematic collection strategy with word-of-mouth contributions made by interested individuals who identified relevant work that we initially overlooked.

@@

```{r data-oarch}
read_csv("https://github.com/zackbatist/open-archaeo/raw/2023-08-29/open-archaeo.csv") %>%
  mutate(category = na_if(category, "?")) ->
  oarch

@@

```{r tbl-repo-licenses}
#| tbl-cap: Summary of licenses used by projects with GitHub repositories.
oarch |>
  hoist(gh_repo_info, license = list("license", 1, "name")) |>
  count(license) |>
  mutate(license = replace_na(license, "None detected")) |>
  arrange(-n) |>
  gt() |>
    cols_label(license = "License", n = "N")
```
